Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 method.tex
Demoted some subsections to subsubsections
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1036 ccdd05d5-56c1-461a-bf98-85f6876523b4
Abbreviation already defined
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1038 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsection{Selectively reducing the sample rate of the data and templates}

@@

\subsection{Reducing the number of filters with the \SVD{}}

@@

\subsection{Early-warning output}

@@

The conventional \TD{} method consists of a bank of \fir{} filters, or sliding-window dot products.  If there are $\numtmps$ templates, each $\tmpsamps$ samples in length, then each filter requires $M N$ multiplications and additions per sample, or $2 \numtmps \tmpsamps f^0$ floating point operations per second (\flops) at a sample rate $f^0$.

>>>>

\subsubsection{Selectively reducing the sample rate of the data and templates}

@@

\subsubsection{Reducing the number of filters with the \SVD{}}

@@

\subsubsection{Early-warning output}

@@

The conventional \TD{} method consists of a bank of \fir{} filters, or sliding-window dot products.  If there are $\numtmps$ templates, each $\tmpsamps$ samples in length, then each filter requires $M N$ multiplications and additions per sample, or $2 \numtmps \tmpsamps f^0$ \flops\ at a sample rate $f^0$.
